NFC and burnout in teachers - A replication and extension study

### 2021-09-03 Manuscript/Manuscript.Rmd
updated plots

  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Burnout", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 0.8, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       theme = "colorblind" # select appropriate colour scheme
                       )
```

@@

>>>>

  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```

@@

```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE}

  # Visualize the results

  fit2_plot <- semPaths(fit2, what = "par",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edge.label.cex = 1, # size of the parameters
                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
  )
```
